\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
Jsuis tanné

A little bit less than half of the articles favoured a static approach to the
recognition of design motifs.

@@

>>>>

Choosing a specific type of analysis tels a lot about the associated technique.
Static analysis is useful when trying to extract structural and semantic
information about a program while dynamic analysis makes it easier to get
information about the behaviour of an algorithm.

The analysis type also affect the kind of tool the algorithm is implemented
in.
In fact dynamic analysis requires much more processing time due to the
profiling aspect associated with it.
This effectively prevent the inclusion of detection algorithm as a realtime
programing aid.

A little bit less than half of the articles favoured a static approach to the
recognition of design motifs, while the other half had a dynamic aspect to
their detection methods.

@@

For structural patterns, a static analysis can be said to be efficient enough.
More than half the detection method used such an analysis with good results

For behavioural pattern, static analysis migh be sufficient but a majority of
article includes a dynamic component to the anaylis.
Tsantalis et al.[325] had good result with their graph similarity scoring
approach for detecting structural and behavioural pattern with a static method.

Creationnal patterns show an interesting distribution of the analysis types.
In fact, it could be said that their identification is difficult with
 a dynamic analysis alone.
Strangely though, a high proportion of article report the recognition of
creationnal design patterns with only a static analysis.
